---
title: "Visualize COVID-19 Tends"
author: "Damiano Fantini"
date: "`r Sys.Date()`"
output: html_document
vignette: >
  %\VignetteIndexEntry{Visualize COVID-19 Tends}
  %\VignetteEngine{knitr::rmarkdown}
  %\usepackage[utf8]{inputenc}
  %\VignetteDepends{Covid19CasesPlot}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, results = "asis", fig.align = "center", fig.width = 10, fig.height = 14)
```

Covid19DataPlot is an R library aimed at retrieving and visualizing day-by-day COVID-19 data for world countries and US-states. This vignette is illustrating how to use `Covid19DataPlot` to visualize COVID-19 data obtained from the John Hopkins University Data Repository on GitHub.

### Install the library from GitHub.

The `Covid19DataPlot` R library is an open-source software hosted on GitHub (<https://github.com/dami82/Covid19CasesPlot>). To install it, you can use `devtools`.

```{r eval=FALSE}
library(devtools)
devtools::install_github(repo = "dami82/Covid19CasesPlot", build_opts = NULL)
```

### Use the library

**Load the library**.

```{r eval=TRUE}
# Load Covid19DataPlot
library(Covid19CasesPlot)

# Load some other useful libraries 
library(ggplot2)
library(gridExtra)
library(dplyr)
```


**Fetch latest data from the JHU Repo**.

```{r}
# Global data
x1 <- fetch_latest_covid19_data(US.only = FALSE)

# US data
x2 <- fetch_latest_covid19_data(US.only = TRUE)
```


**Get info about dates and/or geo areas**.

```{r}
# Dates
get_available_dates(x1)

# Dates
get_available_geo_areas(x2) %>% utils::head()
```

**Plot COVID-19 data from a list of Countries of interest**.

```{r}
# Build Country Plots
p1 <- plot_covid19_data(covid19.data = x1, geo.area = "Italy", 
                        y.limit = 16000, dth.scale.k = 4)
p2 <- plot_covid19_data(covid19.data = x1, geo.area = "France", 
                        y.limit = 16000, dth.scale.k = 4) 
p3 <- plot_covid19_data(covid19.data = x1, geo.area = "US", 
                        y.limit = 16000, dth.scale.k = 4) 
p4 <- plot_covid19_data(covid19.data = x1, geo.area = "Spain", 
                        y.limit = 16000, dth.scale.k = 4) 
p5 <- plot_covid19_data(covid19.data = x1, geo.area = "Germany", 
                        y.limit = 16000, dth.scale.k = 4)
p6 <- plot_covid19_data(covid19.data = x1, geo.area = "United Kingdom", 
                        y.limit = 16000, dth.scale.k = 4) 

# Put together, visualize
grid.arrange(p1, p4, p2, p5, p3, p6, ncol = 2)
```


**Plot COVID-19 data from a list of US-states of interest**.

```{r}
# Build US-states Plots
pu1 <- plot_covid19_data(covid19.data = x2, geo.area = "Illinois", dth.scale.k = 3)
pu2 <- plot_covid19_data(covid19.data = x2, geo.area = "Michigan", dth.scale.k = 3)
pu3 <- plot_covid19_data(covid19.data = x2, geo.area = "California", dth.scale.k = 3)
pu4 <- plot_covid19_data(covid19.data = x2, geo.area = "New York", dth.scale.k = 3) 
pu5 <- plot_covid19_data(covid19.data = x2, geo.area = "New Jersey", dth.scale.k = 3) 
pu6 <- plot_covid19_data(covid19.data = x2, geo.area = "Massachusetts", dth.scale.k = 3) 

# Put together, visualize
grid.arrange(pu1, pu2, pu3, pu4, pu5, pu6, ncol = 2)
```

More info are available at:

- **Day-by-day COVID-19 Patterns**: <https://www.data-pulse.com/dev_site/covid19/>

- **GitHub (R lib)**: <https://github.com/dami82/Covid19CasesPlot>

- **JHU COVID-19 data**: <https://systems.jhu.edu/research/public-health/ncov/>


